% LaTeX resume using res.cls
\documentclass[line,margin]{res} 
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 

\begin{document}

\name{Jordan I. Walker}
% \address used twice to have two lines of address
\address{1010 Gammon Ln Apt 1, Madison, WI 53719}
\address{email: jiwalker@usgs.gov | phone: 608.370.1908}
 
\begin{resume}
 
\section{PROFILE} My background in computers from early on led to me pursuing a degree in Computer Science, and my continued interest in learning resulted in continuing on for my Graduate degree.  Working with distributed systems on diverse datasets throughout my work and education history prepared me for my present position at the USGS Center for Integrated Data Analytics, where I implement generalized scientific applications for environmental data.
 
\section{EXPERIENCE} 	{\sl Computer Scientist} \hfill June 2010 - Present \\
                US Geological Survey Center for Integrated Analytics, Middleton, WI \\
		{\sl Student Programmer} \hfill Feb 2007 - May 2010 \\
                University of Wisconsin Space Science Data Center, Madison, WI\\
		{\sl System Administrator} \hfill Mar - Dec 2006 \\
	     University of Wisconsin Psychiatry Clinic, Madison, WI \\
		{\sl Computer Operator} \hfill Summer 2005 \\
                Computer Sciences Corporation, Hampton, VA \\
		{\sl Information Systems Intern} \hfill Fall 2003 - Summer 2004 \\
                Wick Building Systems, Inc., Mazomanie, WI
 
\section{EDUCATION} {\sl MS,} Computer Science \\
        	     	University of Wisconsin-Madison -- Madison, WI \\ 
                	2008-2010

		{\sl BS,} Computer Science \\
		University of Wisconsin-Madison -- Madison, WI \\
		2004-2008
  
\section{PUBLICATIONS}
	\begin{itemize} \itemsep -2pt
	 \item Ormont, J. and Walker, J. and Banerjee, S. and Sridharan, A. and Seshadri, M. and Machiraju, S., 2008, {\sl A City-wide Vehicular Testbed for Wide-area Wireless Experimentation.} WiNTECH.
    	 \item Ormont, J. and Walker, J. and Banerjee, S., 2008, {\sl Continuous Monitoring of Wide-area Wireless Networks: Data Collection and Visualization.} Sigmetrics Performance Evaluation Review.
	\item Patro, A. and Ma, Y. and Panahi, F. and Walker, J. and Banerjee, S., 2011, {\sl A system for audio signalling based NAT Traversal} COMSNETS.
	\item Blodgett, D.L., Booth, N.L., Kunicki, T.C., Walker, J.I., and Viger, R.J., 2011, {\sl Description and testing of the Geo Data Portal: Data integration framework and Web processing services for environmental science collaboration} U.S. Geological Survey Open-File Report 2011–1157, 9 p.
	\item Blodgett, D.L., Booth, N.L., Kunicki, T.C., Walker, J.I., Lucido, J., 2012, {\sl Description of the U.S. Geological Survey Geo Data Portal Data Integration Framework} IEEE JSTARS, in press.
	\end{itemize}

\end{resume}
\end{document}
